\LARGE \bf Human-Robot Interaction: Tackling the AI Challenges

### 2014-05-05 paper.tex
Adjustment to spark-oro figure

    \node[draw=none] at (0,0) {\includegraphics[width=0.8\columnwidth]{spark-oro-notext.pdf}};

@@

    \node[box=16cm, minimum height=3cm, dotted, thick, rounded corners] at (0,-3.75) (spark) {};
    \path (spark.north) edge[->] node[align=left,anchor=west] {Symbolic\\facts} (oro.south);

    \node[anchor=north] at (-4.5,-4.5) {Relative locations};
    \node[anchor=north] at (-1.5,-4.5) {Spatial relations};
    \node[anchor=north] at (1.5,-4.5) {Visibility};
    \node[anchor=north] at (4.8,-4.5) {Reachability};

>>>>

    \node[draw=none] at (0,-1) {\includegraphics[width=0.8\columnwidth]{spark-oro-notext.pdf}};

@@

    \node[box=16cm, minimum height=3.5cm, dotted, thick, rounded corners] at (0,-3.75) (spark) {};
    \path (spark.north) edge[->] node[align=left,anchor=west] {Symbolic\\facts} (oro.south);

    \node[anchor=north] at (-5.5,-4.5) {a) Agent-independent\\locations};
    \node[anchor=north] at (-1.8,-4.5) {b) Agent-dependent\\placements};
    \node[anchor=north] at (1.5,-4.5) {c) Visibility};
    \node[anchor=north] at (5.3,-4.5) {d) Reachability};
